Phenotypic evolution is more constrained in simpler food webs

### 2018-11-22 manuscript.Rmd
update figure legends based on Jordi's comments.

**Figure \ref{fig:UV_Landscape}**: Adaptive landscape of gall midge phenotypes in complex vs. simple food webs. Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C). Solid lines represent selection experienced in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. Solid yellow lines represent selection imposed by larval parasitoids in the complex food web. Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.

**Figure \ref{fig:MV_Landscape}**: Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs. simple food webs. Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C). Selection favors trait integration for each combination of traits in simple food webs, whereas there is no strong evidence for trait integration in complex food webs. Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.

>>>>

**Figure \ref{fig:UV_Landscape}**: Adaptive landscape of gall midge phenotypes in complex vs. simple food webs. Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C). Solid lines represent selection experienced in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates to show the uncertainty in selection. For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates. Solid yellow lines represent selection imposed by larval parasitoids in the complex food web. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.

**Figure \ref{fig:MV_Landscape}**: Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs. simple food webs. Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C). Note the flat landscape in mean larval survival for clutch size and oviposition preference in more complex food webs, whereas all three traits shape the adaptive landscape in simpler food webs. This indicates that selection favors trait integration for each combination of traits in simpler food webs, whereas there is no strong evidence for trait integration in more complex food webs. Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
